Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-18 proposalPres.tex
Updated proposalPres.tex
Fixed errors in sim result tables

Added slide about ARX model representation in MATLAB

\begin{frame}{Model Equations}
	\begin{block}{}
		\begin{itemize}
			\item Transfer Function Model: 
			\begin{equation}
				\frac{Y(s)}{U_A(s)} = \frac{b_{n}s^{n} + b_{n-1}s^{n-1} + ... + b_1s + b_0}{a_{m}s^{m} + a_{m-1}s^{m-1} + ... + a_1s + a_0}
			\end{equation}
			where m = number of poles and n = number of zeros
			\item ARX Model: 
			\begin{equation}
				A(z)y(t) = B(z)u(t) + e(t)
			\end{equation}
		\end{itemize}
	\end{block}
\end{frame}

@@

  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$&$a_{19}$&$a_{20}$\\
      \midrule
      1.949E-16 & 1.455E-14 & 8.797E-13 & 2.304E-11 & 9.041E-10 & 9.01E-9 & 2.714E-7 & 9.241E-7 & 1.946E-5 & 3.889E-5 & 0.0005721 & 0.0008035 & 0.008695 & 0.008922 & 0.07499 & 0.05422 & 0.3631 & 0.1693 & 0.9394 & 0.2118 & 1\\
      \bottomrule
    \end{tabular}}

% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque A}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & 3.44E-16 \\
% 				b_1 & -2.203E-15 \\
% 				b_2 & 1.24E-13 \\
% 				b_3 & 5.975E-13 \\
% 				b_4 & 3.001E-12 \\
% 				b_5 & 5.23E-12 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 1.949E-16 \\
% 				a_1 & 1.455E-14 \\
% 				a_2 & 8.797E-13 \\
% 				a_3 & 2.304E-11 \\
% 				a_4 & 9.041E-10 \\
% 				a_5 & 9.01E-9 \\
% 				a_6 & 2.714E-7 \\
% 				a_7 & 9.241E-7 \\
% 				a_8 & 1.946E-5 \\
% 				a_9 & 3.889E-5 \\
% 				a_{10} & 0.0005721 \\
% 				a_{11} & 0.0008035 \\
% 				a_{12} & 0.008695 \\
% 				a_{13} & 0.008922 \\
% 				a_{14} & 0.07499 \\
% 				a_{15} & 0.05422 \\
% 				a_{16} & 0.3631 \\
% 				a_{17} & 0.1693 \\
% 				a_{18} & 0.9394 \\
% 				a_{19} & 0.2118 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} 
% 		\end{tabular}
% 	\end{block}
% \end{minipage}%
% \hfill%
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque B}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & -6.645E-15 \\
% 				b_1 & 2.161E-14 \\
% 				b_2 & -2.605E-14 \\
% 				b_3 & -4.744E-13 \\
% 				b_4 & -1.813E-13 \\
% 				b_5 & -4.858E-12 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 2.92E-15 \\
% 				a_1 & 2.758E-13 \\
% 				a_2 & 1.761E-11 \\
% 				a_3 & 4.228E-10 \\
% 				a_4 & 1.422E-8 \\
% 				a_5 & 1.561E-7 \\
% 				a_6 & 1.501E-6 \\
% 				a_7 & 8.426E-6 \\
% 				a_8 & 5.981E-5 \\
% 				a_9 & 0.0002016 \\
% 				a_{10} & 0.001226 \\
% 				a_{11} & 0.002649 \\
% 				a_{12} & 0.01456 \\
% 				a_{13} & 0.02044 \\
% 				a_{14} & 0.104 \\
% 				a_{15} & 0.09228 \\
% 				a_{16} & 0.4417 \\
% 				a_{17} & 0.2257 \\
% 				a_{18} & 1.025 \\
% 				a_{19} & 0.2305 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} 
% 		\end{tabular}
% 	\end{block}
% \end{minipage}
\end{frame}

\begin{frame}{Manual Steering System Transfer Function}
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque A}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & 6.516E4 \\
% 				b_1 & -2.944E5 \\
% 				b_2 & 2.328E5 \\
% 				b_3 & -2.487E5 \\
% 				b_4 & 8.25E4 \\
% 				b_5 & -3.038E4 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 1.224E5 \\
% 				a_1 & 4.227E5 \\
% 				a_2 & 2.202E6 \\
% 				a_3 & 3.54E6 \\
% 				a_4 & 7.98E6 \\
% 				a_5 & 7.62E5 \\
% 				a_6 & 1.071E7 \\
% 				a_7 & 6.745E6 \\
% 				a_8 & 6.85E6 \\
% 				a_9 & 3.006E6 \\
% 				a_{10} & 2.365E6 \\
% 				a_{11} & 7.37E5 \\
% 				a_{12} & 4.669E5 \\
% 				a_{13} & 1.021E5 \\
% 				a_{14} & 5.319E4 \\
% 				a_{15} & 7752 \\
% 				a_{16} & 3353 \\
% 				a_{17} & 287.5 \\
% 				a_{18} & 102.4 \\
% 				a_{19} & 3.653 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}%
% \hfill%
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque B}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & 1.209E4 \\
% 				b_1 & 1.855E5 \\
% 				b_2 & -2.801E5 \\
% 				b_3 & 4.72E5 \\
% 				b_4 & -3.976E4 \\
% 				b_5 & 7.693E4 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 4.687E4 \\
% 				a_1 & 7.037E5 \\
% 				a_2 & 2.624E6 \\
% 				a_3 & 6.133E6 \\
% 				a_4 & 1.197E7 \\
% 				a_5 & 1.487E7 \\
% 				a_6 & 1.887E7 \\
% 				a_7 & 1.446E7 \\
% 				a_8 & 1.314E7 \\
% 				a_9 & 7.01E6 \\
% 				a_{10} & 4.79E6 \\
% 				a_{11} & 1.886E6 \\
% 				a_{12} & 9.836E5 \\
% 				a_{13} & 2.937E5 \\
% 				a_{14} & 1.149E5 \\
% 				a_{15} & 2.617E4 \\
% 				a_{16} & 7205 \\
% 				a_{17} & 1232 \\
% 				a_{18} & 200 \\
% 				a_{19} & 23.54 \\
% 				a_{20} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}
\end{frame}

@@

\begin{frame}{By-Wire Acceleration System Transfer Function}
	\begin{block}{Fourth-Order ARX Model}
		\begin{equation}
			A(z)y(t) = B(z)u(t) + e(t)
		\end{equation}
		%
		where, 
		%
		\begin{equation}
			A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
		\end{equation}
		\begin{equation}
			B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
		\end{equation}
		\begin{equation}
			B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
		\end{equation}
	\end{block}
\end{frame}

\begin{frame}{Manual Acceleration System Transfer Function}
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque A}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & -5.741E6 \\
% 				b_1 & -2.644E7 \\
% 				b_2 & -2.797E6 \\
% 				b_3 & -1.304E7 \\
% 				b_4 & -3.203E6 \\
% 				b_5 & -1.159E6 \\
% 				b_6 & -5.519E5 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 2.307E7 \\
% 				a_1 & 8.369E7 \\
% 				a_2 & 9.137E8 \\
% 				a_3 & 1.992E9 \\
% 				a_4 & 3.753E9 \\
% 				a_5 & 5.454E9 \\
% 				a_6 & 5.548E9 \\
% 				a_7 & 5.869E9 \\
% 				a_8 & 3.453E9 \\
% 				a_9 & 3.161E9 \\
% 				a_{10} & 1.54E9 \\
% 				a_{11} & 9.654E8 \\
% 				a_{12} & 3.556E8 \\
% 				a_{13} & 1.789E8 \\
% 				a_{14} & 5.082E7 \\
% 				a_{15} & 2.071E7 \\
% 				a_{16} & 4.569E6 \\
% 				a_{17} & 1.498E6 \\
% 				a_{18} & 2.553E5 \\
% 				a_{19} & 6.532E4 \\
% 				a_{20} & 8443 \\
% 				a_{21} & 1559 \\
% 				a_{22} & 147.3 \\
% 				a_{23} & 15.5 \\
% 				a_{24} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}%
% \hfill%
% \begin{minipage}[t]{0.48\linewidth}
% 	\begin{block}{Torque B}
% 		\tiny
% 		\begin{tabular}{ cc }   % top level tables, with 2 columns
% 			% leftmost table of the top level table
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				b_0 & -4.159E6 \\
% 				b_1 & 1.851E6 \\
% 				b_2 & -4.457E6 \\
% 				b_3 & 9.043E5 \\
% 				b_4 & -7.45E5 \\
% 				b_5 & 1.865E5 \\
% 				b_6 & -1.545E4 \\
% 				\hline
% 			\end{tabular} &  % starting rightmost sub table
% 			% table 2
% 			\begin{tabular}{ |c|c| } 
% 				\hline
% 				a_0 & 5.224E6 \\
% 				a_1 & 4.205E7 \\
% 				a_2 & 1.429E8 \\
% 				a_3 & 3.233E8 \\
% 				a_4 & 5.444E8 \\
% 				a_5 & 7.326E8 \\
% 				a_6 & 8.247E8 \\
% 				a_7 & 7.402E8 \\
% 				a_8 & 6.301E8 \\
% 				a_9 & 3.99E8 \\
% 				a_{10} & 2.731E8 \\
% 				a_{11} & 1.264E8 \\
% 				a_{12} & 7.223E7 \\
% 				a_{13} & 2.48E7 \\
% 				a_{14} & 1.216E7 \\
% 				a_{15} & 3.084E6 \\
% 				a_{16} & 1.324E6 \\
% 				a_{17} & 2.422E5 \\
% 				a_{18} & 9.264E4 \\
% 				a_{19} & 1.159E4 \\
% 				a_{20} & 4003 \\
% 				a_{21} & 307.4 \\
% 				a_{22} & 96.87 \\
% 				a_{23} & 3.451 \\
% 				a_{24} & 1 \\
% 				\hline
% 			\end{tabular} \\
% 		\end{tabular}
% 	\end{block}
% \end{minipage}
\end{frame}

>>>>

\begin{frame}{Model Equations}
	\begin{block}{Model Equations}
		\begin{itemize}
			\item Transfer Function Model: 
			\begin{equation}
				\frac{Y(s)}{U_A(s)} = \frac{b_{n}s^{n} + b_{n-1}s^{n-1} + ... + b_1s + b_0}{a_{m}s^{m} + a_{m-1}s^{m-1} + ... + a_1s + a_0}
			\end{equation}
			where m = number of poles and n = number of zeros
			\item ARX Model: 
			\begin{equation}
				A(z)y(t) = B(z)u(t) + e(t)
			\end{equation}
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Model Equations}
	\tiny	
	\begin{block}{ARX Model MATLAB Representation}
		The polynomial equation for an ARX Model is:
		\begin{equation}
			y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)
		\end{equation}
		where na, nb, and nk are the system’s number of poles, number of zeros, and the system dead time, respectively
		MATLAB represents the ARX Model with the following equation:
		\begin{equation}
			A(z)y(t) = B(z)u(t - n_k) + e(t)
		\end{equation}
		where z is a delay operator and 
		\begin{equation}
			A(z) = 1 + a_1z^{-1} + ... + a_{na}z^{-n_a}
		\end{equation}
		\begin{equation}
			B(z) = b_1 + b_2z^{-1} + ... + b_{nb}z^{-n_b}
		\end{equation}
		For MISO systems, MATLAB uses the following equation to represent the ARX Model:
		\begin{equation}
			A(z)y(t) = B_1(z)u_1(t - nk_{1}) + B_2(z)u_2(t - nk_{2}) + ... + B_{nu}(z)u_{nu}(t - nk_{nu})
		\end{equation}
		where nu is the number of system inputs
	\end{block}
\end{frame}

@@

\begin{block}{Torque Voltage A}
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
      \midrule
      1.949E-16 & 1.455E-14 & 8.797E-13 & 2.304E-11 & 9.041E-10 & 9.01E-9 & 2.714E-7 & 9.241E-7 & 1.946E-5 & 3.889E-5 & 0.0005721 & 0.0008035 & 0.008695 & 0.008922 & 0.07499 & 0.05422 & 0.3631 & 0.1693 & 0.9394 & 0.2118 & 1\\
      \bottomrule
    \end{tabular}}

    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
      \midrule
      3.44E-16 & -2.203E-15 & 1.24E-13 & 5.975E-13 & 3.001E-12 & 5.23E-12\\
      \bottomrule
    \end{tabular}}
\end{block}
\begin{block}{Torque Voltage B}
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
      \midrule
      2.92E-15 & 2.758E-13 & 1.761E-11 & 4.228E-10 & 1.422E-8 & 1.561E-7 & 1.501E-6 & 8.426E-6 & 5.981E-5 & 0.0002016 & 0.001226 & 0.002649 & 0.01456 & 0.02044 & 0.104 & 0.09228 & 0.4417 & 0.2257 & 1.025 & 0.2305 & 1\\
      \bottomrule
    \end{tabular}}
    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
      \midrule
      -6.645E-15 & 2.161E-14 & -2.605E-14 & -4.744E-13 & -1.813E-13 & -4.858E-12\\
      \bottomrule
    \end{tabular}}
\end{block}  
\end{frame}

\begin{frame}{Manual Steering System Transfer Function}

\begin{block}{Torque Voltage A}
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
      \midrule
      1.224E5 & 4.227E5 & 2.202E6 & 3.54E6 & 7.98E6 & 7.62E5 & 1.071E7 & 6.745E6 & 6.85E6 & 3.006E6 & 2.365E6 & 7.37E5 & 4.669E5 & 1.021E5 & 5.319E4 & 7752 & 3353 & 287.5 & 102.4 & 3.653 & 1\\
      \bottomrule
    \end{tabular}}

    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
      \midrule
      6.516E4 & -2.944E5 & 2.328E5 & -2.487E5 & 8.25E4 & -3.038E4\\
      \bottomrule
    \end{tabular}}
\end{block}
\begin{block}{Torque Voltage B}
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
      \midrule
      4.687E4 & 7.037E5 & 2.624E6 & 6.133E6 & 1.197E7 & 1.487E7 & 1.887E7 & 1.446E7 & 1.314E7 & 7.01E6 & 4.79E6 & 1.886E6 & 9.836E5 & 2.937E5 & 1.149E5 & 2.617E4 & 7205 & 1232 & 200 & 23.54 & 1\\
      \bottomrule
    \end{tabular}}
    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
      \midrule
      1.209E4 & 1.855E5 & -2.801E5 & 4.72E5 & -3.976E4 & 7.693E4\\
      \bottomrule
    \end{tabular}}
\end{block}
\end{frame}

@@

\begin{frame}{By-Wire Acceleration System Transfer Function}
	\begin{block}{Fourth-Order ARX Model}
		\begin{equation}
			A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
		\end{equation}
		%
		where na = 4, nb = 4, nk = 0, and, 
		%
		\begin{equation}
			A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
		\end{equation}
		\begin{equation}
			B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
		\end{equation}
		\begin{equation}
			B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
		\end{equation}
	\end{block}
\end{frame}

\begin{frame}{Manual Acceleration System Transfer Function}
\begin{block}{Torque Voltage A}
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{25}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
      \midrule
      2.307E7 & 8.369E7 & 9.137E8 & 1.992E9 & 3.753E9 & 5.454E9 & 5.548E9 & 5.869E9 & 3.453E9 & 3.161E9 & 1.54E9 & 9.654E8 & 3.556E8 & 1.789E8 & 5.082E7 & 2.071E7 & 4.569E6 & 1.498E6 & 2.553E5 & 6.532E4 & 8443 & 1559 & 147.3 & 15.5 & 1\\
      \bottomrule
    \end{tabular}}

    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{7}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
      \midrule
      -5.741E6 & -2.644E7 & -2.797E6 & -1.304E7 & -3.203E6 & -1.159E6 & -5.519E5\\
      \bottomrule
    \end{tabular}}
\end{block}
\begin{block}{Torque Voltage B}
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{25}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$&$a_{21}$&$a_{22}$&$a_{23}$&$a_{24}$\\
      \midrule
      5.224E6 & 4.205E7 & 1.429E8 & 3.233E8 & 5.444E8 & 7.326E8 & 8.247E8 & 7.402E8 & 6.301E8 & 3.99E8 & 2.731E8 & 1.264E8 & 7.223E7 & 2.48E7 & 1.216E7 & 3.084E6 & 1.324E6 & 2.422E5 & 9.264E4 & 1.159E4 & 4003 & 307.4 & 96.87 & 3.451 & 1\\
      \bottomrule
    \end{tabular}}

    	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{7}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$&$b_6$\\
      \midrule
      -4.159E6 & 1.851E6 & -4.457E6 & 9.043E5 & -7.45E5 & 1.865E5 & -1.545E4\\
      \bottomrule
    \end{tabular}}
\end{block}
\end{frame}
